%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\documentclass[11pt, a4paper]{awesome-cv}

\geometry{left=2cm, top=1cm, right=2cm, bottom=2cm, footskip=.5cm}
\setlength{\parskip}{0.5em}

\fontdir[fonts/]
\colorlet{awesome}{awesome-red}

\setbool{acvSectionColorHighlight}{true}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%-------------------------------------------------------------------------------
\name{Ioan Andrés}{Muñoz}
\position{Web Developer{\enskip\cdotp\enskip}English Teacher}
\address{Pitalito, Huila, Colombia}

\mobile{(+57) 314-350-7147 / (+57) 317-868-4451}
\email{jaguerx88@gmail.com}
\github{IAM-DEV88}
\homepage{iamjaguer.netlify.app}

%-------------------------------------------------------------------------------
\begin{document}

\makecvheader[C]

\makecvfooter
  {\today}
  {Ioan Andrés Muñoz~~~·~~~Curriculum Vitae}
  {\thepage}

%-------------------------------------------------------------------------------
%	PROFESSIONAL PROFILE
%-------------------------------------------------------------------------------
\cvsection{Professional Profile}

Bilingual professional with experience in web development, English teaching, and international customer support. I combine technical skills (TypeScript, React, Node.js, cloud computing) with conversational English communication abilities to thrive in multicultural environments and multidisciplinary teams. I am interested in solving real problems through clear and functional technology, and sharing knowledge in a practical way so others can grow too. I seek roles where I can contribute both from code and bilingual communication.

%-------------------------------------------------------------------------------
%	DEVELOPMENT EXPERIENCE
%-------------------------------------------------------------------------------
\cvsection{Development Experience}

\cvevent{\textbf{Fullstack Developer}}{ - Freelance - }{\textbf{July 2019 -- Present}}{}
\begin{itemize}
  \item Built full-stack web applications with TypeScript, React, and Node.js.
  \item Integrated cloud services, authentication, payment gateways, and artificial intelligence.
  \item Automated deployments on Netlify and Vercel with serverless functions.
\end{itemize}

\cvevent{\textbf{Frontend Developer}}{ - CLAROS SOLUCIONES - }{\textbf{October 2019 -- February 2023}}{}
\begin{itemize}
  \item Built user interfaces with React and Vue, prioritizing usability and performance.
  \item Collaborated directly with design and backend teams to deliver complete features.
  \item Optimized accessibility, load times, and code maintainability.
\end{itemize}

%-------------------------------------------------------------------------------
%	BILINGUAL EXPERIENCE
%-------------------------------------------------------------------------------
\cvsection{Bilingual Experience}

\cvevent{\textbf{Bilingual Operations Specialist}}{ - Incall - }{\textbf{August 2021 -- June 2023}}{}
\begin{itemize}
  \item Provided support in English for clients in Canada and the United States.
  \item Processed quotes, tracked shipments, and resolved incidents.
\end{itemize}

\cvevent{\textbf{Bilingual Advisor}}{ - Teleperformance - }{\textbf{November 2020 -- April 2021}}{}
\begin{itemize}
  \item Provided phone and administrative support in English for international inquiries.
  \item Recorded information following security and encryption protocols.
\end{itemize}

%-------------------------------------------------------------------------------
%	TEACHING EXPERIENCE
%-------------------------------------------------------------------------------
\cvsection{Teaching Experience}

\cvevent{\textbf{English Teacher}}{ - Universal Centro de Idiomas - }{\textbf{August 2024 -- December 2024}}{}
\begin{itemize}
  \item Taught basic and intermediate English to teenagers and adults, with emphasis on oral communication and reading comprehension.
  \item Designed lesson plans tailored to each group's level and pace.
  \item Monitored individual progress and provided constant feedback to build confidence and fluency.
\end{itemize}

\cvevent{\textbf{English Teacher}}{ - Institución Educativa Los Cauchos, San Agustín - }{\textbf{May 2009 -- June 2009}}{}
\begin{itemize}
  \item Taught basic English to high school students in a rural area.
  \item Assessed and monitored learning using available classroom resources.
\end{itemize}

%-------------------------------------------------------------------------------
%	PRIOR EXPERIENCE
%-------------------------------------------------------------------------------
\cvsection{Prior Experience}

\cvevent{\textbf{Systems Technician}}{ - CONSORCIO WIFI - }{\textbf{August 2020 -- December 2019}}{}
\begin{itemize}
  \item Installed and maintained WiFi connection points in rural areas.
  \item Recorded and validated technical data in the field.
\end{itemize}

\cvevent{\textbf{Surveyor and Statistics Assistant}}{ - Alcaldía Municipal de Pitalito - }{\textbf{October 2018 -- December 2018}}{}
\begin{itemize}
  \item Collected and digitized data with a high degree of accuracy.
\end{itemize}

\cvevent{\textbf{Administrative Assistant}}{ - Sistemas Avanzados en Telecomunicaciones S.A.S. - }{\textbf{January 2017 -- June 2017}}{}
\begin{itemize}
  \item Coordinated budgets, contracts, and inventory management.
\end{itemize}

\cvevent{\textbf{Cashier and Warehouse Assistant}}{ - Estanco San Diego, Popayán - }{\textbf{November 2014 -- September 2015}}{}
\begin{itemize}
  \item Customer service, inventory management, and order preparation.
\end{itemize}

\cvevent{\textbf{Sales Advisor}}{ - Claro Colombia, Bogotá - }{\textbf{February 2012 -- May 2012}}{}
\begin{itemize}
  \item Customer support and data entry into systems following internal manuals.
\end{itemize}

\cvevent{\textbf{Systems Technician}}{ - Café Internet Fenix.net, San Agustín - }{\textbf{November 2009 -- September 2010}}{}
\begin{itemize}
  \item Hardware and software maintenance. User support and technical assistance.
\end{itemize}

%-------------------------------------------------------------------------------
%	FEATURED PROJECTS
%-------------------------------------------------------------------------------
\cvsection{Featured Projects}

\divider

\cvevent{\textbf{AgendaYa}}{ - {Business Booking \& Discovery App} - }{\href{https://agendalisto.com} - {Visit Site}}
\begin{itemize}
  \item Full platform for local businesses to publish services and clients to book appointments online.
  \item Dynamic blog with AI-assisted content generation for SEO and organic acquisition.
  \item Payment gateways (PayPal, Wompi), OAuth authentication, real-time notifications, and admin dashboard with metrics.
  \item Referral system, gift codes, and chatbot with language model.
  \item Built with \textbf{React 19}, \textbf{TypeScript}, \textbf{Vite}, \textbf{Redux Toolkit}, \textbf{Supabase}, and \textbf{Tailwind CSS}.
\end{itemize}

\divider

\cvevent{\textbf{Lexigo}}{ - {English Learning App} - }{\href{https://lexigo.app} - {Visit Site}}
\begin{itemize}
  \item Web platform for learning English with structured lessons, interactive exercises, and progress tracking.
  \item Built with \textbf{React}, \textbf{TypeScript}, \textbf{Supabase}, and AI integration for personalized feedback.
  \item Course system, achievements, study streaks, and tutoring sessions.
\end{itemize}

\divider

\cvevent{\textbf{Student Management System}}{ - {CRUD Web App} - }{\href{https://iam-dev88.github.io/student-manager/} - {Visit Site}}
\begin{itemize}
  \item Application for registering, querying, updating, and deleting student academic information.
  \item Built with \textbf{React}, \textbf{Redux}, \textbf{Node.js}, \textbf{Express}, and \textbf{MongoDB}.
\end{itemize}

\divider

\cvevent{\textbf{Colmillo de Acero}}{ - {Community \& Raid Management System} - }{\href{https://colmillo.netlify.app/} - {Visit Site}}
\begin{itemize}
  \item Web platform for gaming community management with over 1000 registered users.
  \item Registration systems, event organization, roles, and permissions.
  \item Automated logic for group assignment and participation tracking.
\end{itemize}

\divider

\cvevent{\textbf{Shop Admin System}}{ - {Store Administration Panel} - }{\href{https://github.com/IAM-DEV88/AdminTiendaWeb} - {Visit GitHub}}
\begin{itemize}
  \item Admin panel for inventory and sales management.
  \item Built with \textbf{PHP}, \textbf{MySQL}, and \textbf{JavaScript}.
\end{itemize}

%-------------------------------------------------------------------------------
%	EDUCATION
%-------------------------------------------------------------------------------
\cvsection{Education}

\begin{itemize}
  \item \textbf{Systems Technician}, Instituto José Celestino Mutis
  \item \textbf{Administrative Management Technologist}, SENA
  \item \textbf{Fullstack Development}, Platzi
\end{itemize}

%-------------------------------------------------------------------------------
%	SKILLS
%-------------------------------------------------------------------------------
\cvsection{Skills}

\begin{cvskills}
  \cvskill
    {Languages}
    {Spanish - Native \quad English - Conversational (B2)}
  \cvskill
    {Communication}
    {Communicative teaching, bilingual customer support, material development, multicultural teamwork}
  \cvskill
    {Frontend}
    {TypeScript, React, Vite, Tailwind CSS, HTML, CSS, Vue}
  \cvskill
    {Backend}
    {Node.js, Express, Supabase, PostgreSQL, MongoDB, PHP, MySQL}
  \cvskill
    {DevOps}
    {Git, GitHub Actions, Netlify, Vercel, Google Cloud}
  \cvskill
    {AI \& Assistance}
    {OpenCode (TUI), AI code assistants, language models (Groq, OpenAI), content generation}
  \cvskill
    {Other}
    {LUA, Technical SEO, PWAs, Discord API, communicative teaching, didactic materials}
\end{cvskills}

%-------------------------------------------------------------------------------
\end{document}
